Playing against Nature: causal discovery for decision making under uncertainty

### 2018-05-22 Segundo_Semestre/CausalML_Workshop/Paper_long_version.tex
Correcciones Hugo: en related work

Several algorithms exists for finding the best arm in a multi-arm bandit, such as \cite{bubeck2009pure}, \cite{audibert2010best}, \cite{gabillon2012best}, \cite{agarwal2014taming} , \cite{jamieson2014lil},  \cite{jamieson2014best},  \cite{ortega2014generalized}, \cite{chen2015optimal},\cite{carpentier2016tight},  \cite{russo2016simple},  \cite{kaufmann2016complexity}, but none of this works consider causal-governed environments.

Up to our current knowledge \cite{lattimoreNIPS2016} is the first paper to consider causal relations between the effects of actions. They consider a decision maker who must choose the best among several possible interventions on a given, and fully known, causal model. The optimality of the action in this context is in terms of the minimal regret. The case where the causal model is not known is left as future work.

>>>>

Several algorithms exists for finding the best arm in a multi-arm bandit, such as those described in \cite{bubeck2009pure}, \cite{audibert2010best}, \cite{gabillon2012best}, \cite{agarwal2014taming} , \cite{jamieson2014lil},  \cite{jamieson2014best},  \cite{ortega2014generalized}, \cite{chen2015optimal},\cite{carpentier2016tight},  \cite{russo2016simple},  \cite{kaufmann2016complexity}, but none of these works consider causal-governed environments.

Up to our current knowledge \cite{lattimoreNIPS2016} is the first paper to consider causal relations between the effects of actions. They consider a decision maker who must choose the best among several possible interventions on a given causal model. The optimality of the action in this context is in terms of the minimal regret. The case where the causal model is not known is left as future work.
